---
title: "Lecture notes"
---
 

+ Topic 1: Introduction to Statistics & Describing Data with Graphs/Numerical Measures
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 1.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

+ Topic 2: Introduction to Probability
  + Part I: Probability
    + Basic definitions in probability
    + Counting rules for calculating probabilities 
    + Event Relations and Probability Rules
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 2_1.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + Part II : Conditional Probability
    + Definition of conditional probability 
    + Bayes Rule
    + Law of Total Probability
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 2_2.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```


+ Topic 3: Random Variables and Important Probability Distributions
  + What is Random Variable and its Distribution? 
  + Discrete random variable and Important discrete distribution
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 3_1.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + Continuous random variable and Important continuous distribution
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 3_2.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```


+ Topic 4: Sampling Distribution and Large-Sample Estimation
  + Central Limit Theorem for Sampling Distribution
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 4_1.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + Large-Sample estimation (point estimation and confidence interval)
    + One population mean
    + Difference between two population means
    + One population proportion
    + Difference between two population proportions
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 4_2.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```   


+ Topic 5: Hypothesis Testing
  + Test about a population mean
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 5_1.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```   

  + Test about the difference between two population means
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 5_2.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```   


  + Test about a population proportion
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 5_3.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```   

  + Test about the difference between two population proportions
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 5_4.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```     
  
+ Topic 6: Correlation and Simple Linear Regression
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 6.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```   
    